Innovations Report: Procedural Fur System

### 2018-03-19 docs/paper.tex
docs tweaks

After I had implemented some of the features Alin requested, I decided that the system was in a satisfactory state for the purposes of this assignment. The following Figures~\ref{figure:screenshots} and ~\ref{figure:screenshot_gui} show examples of the kind of visual output my system is capable of producing, and the accompanying node graph setup used to create them.

>>>>

After I had implemented some of the features Alin requested, I decided that the system was in a satisfactory state for the purposes of this assignment. The following Figures~\ref{figure:screenshots} and~\ref{figure:screenshot_gui} show examples of the kind of visual output my system is capable of producing, and the accompanying node graph setup used to create them.
